\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

\name{Sourabh Sarkar}
\address{Email : emailaddr}
\address{Phone : mobno}
\address{address}

\begin{document}

\begin{rSection}{Objective}
	
	\vskip 2 mm
	
	An analytical and technically efficient Computer Science engineering graduate seeking to grow as a software engineer or a technical engineer in the field of Research and Development. 
	
\end{rSection}

\vskip 2 mm


\begin{rSection}{Education}
	
\vskip 2 mm

{\bf Kalinga Institute of Industrial Technology} \hfill {\em 2015 – 2019} \\ 
Computer Science and Engineering\\
Overall CGPA: pc

\vskip 2 mm

{\bf St. Lawrence High School, Kolkata, India} \hfill {\em 2013 - 2015} \\ 
West Bengal Council of Higher Secondary Education(Science)\\
Percentage: pc\% 

\vskip 2 mm

{\bf South Point High School, Kolkata, India} \hfill {\em  2000 - 2013} \\ 
West Bengal Board of Secondary Education \\
Percentage: pc\% 

\end{rSection}

\vskip 2 mm

\begin{rSection}{Work Experience}
	
	\vskip 2 mm

\begin{rSubsection}{Accenture Pvt. Ltd.}{June 2019 - Present}{Application Development Associate, Java}{Bengaluru, India}
	\item Document Development, Migration, Automation, Configeration and Testing in Quadient.
\end{rSubsection}
	
\begin{rSubsection}{EBIW Info Analytics}{May 2018 - June 2018}{Intern}{Kolkata, India}
\item Made an Airport Guiding Application, using Android, Firebase and NodeJS.
\end{rSubsection}
\end{rSection}

\begin{rSection}{Research Paper}
	
	\vskip 2 mm
	
	{\bf Android based Home Security Systems using Internet of Things(IoT) \newline
		and Firebase}{\hfill \em  2018} 
	
	\vskip 2 mm
	
\end{rSection}

\begin{rSection}{PROJECTS}
	
\vskip 2 mm

\begin{rSubsection}{Android (using MySQL)}{2017}{Android Application Development}{Kolkata, India}
	\item Reminder Alert - Shows notification and rings alarms on given time.   
\end{rSubsection}


\newpage


\begin{rSubsection}{IOT (Using Local Host)}{2016}{Internet of Things}{Bhubaneswar, India}
	\item Medicine pillbox - Sees if patient has taken pill or not. Informs the patient's abnormal heartbeat rate to guardian.   
	
	\vskip 2 mm
	
\end{rSubsection}

\begin{rSubsection}{Smart-Home Auto(IOT 3rd Year Project)}{2018}{Internet of Things}{Bhubaneswar, India}
 \item It Consists of Android Application, Nodemcu (IOT) and Firebase. It was a prototype demonstrating how we can apply home automation at a low cost from scratch.
\vskip 2 mm
\end{rSubsection}

\begin{rSubsection}{Chatting App(using Firebase)}{2019}{Android Application Development}{Bhubaneswar, India}
	\item In this application, the user can send friend request to other users, one user can send text or images and see the current location along with the shortest route only of the people in the friend-list, notification is shown on Friend request sent.  
	\vskip 2 mm
\end{rSubsection}

\end{rSection}

\begin{rSection}{CERTIFICATIONS}

\vskip 2 mm
	
\begin{itemize}
\item {\bf Java.}
\item {\bf Android App Development.}
\item {\bf IOT.}
\item {\bf Python.}
\item {\bf Quadient.}
\end{itemize}
\vskip 2 mm


\end{rSection}

\begin{rSection}{TECHNICAL SKILLS}
	
	\vskip 2 mm

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages &  Java, C, Python.\\
Protocols \& APIs &  JSON \\
Technology & IOT, Firebase, Android App Development and Quadient.\\
Tools & Android Studio, Photoshop\\
Operating System &  Windows XP, Vista, 7, 8, 10

\end{tabular}

	\vskip 2 mm
	
\end{rSection}


\begin{rSection}{SKILLS AND ABILITIES}
	
	\vskip 2 mm
	
	\begin{itemize}
		\item  Good at listening, verbal and written skills.
		\item  Hands on experience working with MS Office, Photoshop.
		\item Ability to work in teams.
		\item Good Time management skills.
	\end{itemize}
		
	\vskip 2 mm
	
\end{rSection}

\vskip 4 mm

\bf {\hfill \em  Sourabh Sarkar.}


\end{document}
